Experiment 2 of 4

### 2018-07-27 experiments/e2/writeup/2018_tidy_version/e2_2018_analysis.Rmd
typos

```{r "load Libraries and source my functions", message=FALSE, echo=FALSE}
library(knitr)
#library(Matrix)
library(ggplot2)
library(xtable)
library(gridExtra)
library(lme4)
library(lmerTest)
library(data.table)
library(dplyr)
library(dtplyr)
#library(pander)
library(LMERConvenienceFunctions)
library(kableExtra)
library(dotwhisker)
library(tidymodels)
library(tidyverse)
library(broom.mixed)
source('../functions/summarySEwithin2.R')
source('../functions/e2-preprocessing.R')
source('../functions/pretty_coef_table.R')
source('../functions/pretty_coef_plot.R')
```

@@

blBarChart = ggplot(bldata) + geom_bar(aes(response_category, group=Number:Vagueness, fill=Vagueness), possition=position_dodge(width=NULL)) +   scale_fill_grey() + xlab(NULL) + ggtitle('Borderline response distribution') + facet_grid(~Number) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.key = element_blank(), legend.position="right", aspect.ratio=1, plot.background = element_rect(fill=NA, color='white'), strip.background=element_blank(), legend.key.size=unit(4, 'mm'), axis.text.x = element_text(angle = 15))

>>>>

```{r "load Libraries and source my functions", message=FALSE, echo=FALSE}
library(knitr)
library(tidyverse)
library(tidymodels)
library(broom.mixed)
library(lme4)
library(lmerTest)
library(dotwhisker)
library(kableExtra)
library(LMERConvenienceFunctions)
library(data.table)
source('../functions/summarySEwithin2.R')
source('../functions/e2-preprocessing.R')
source('../functions/pretty_coef_table.R')
source('../functions/pretty_coef_plot.R')
```

@@

blBarChart = ggplot(bldata) + geom_bar(aes(response_category, group=Number:Vagueness, fill=Vagueness), position=position_dodge(width=NULL)) +   scale_fill_grey() + xlab(NULL) + ggtitle('Borderline response distribution') + facet_grid(~Number) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.key = element_blank(), legend.position="right", aspect.ratio=1, plot.background = element_rect(fill=NA, color='white'), strip.background=element_blank(), legend.key.size=unit(4, 'mm'), axis.text.x = element_text(angle = 15))
